---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(learnr)
library(tidyverse)
library(digest)
#tutorial_options(exercise.timelimit = 10, exercise.checker = checker)
```

# Digital Supply Chain Management 

## Digital Supply Chain Management Pt1

Some basic information about the development of industry and Digital Supply Chain Management emergence can be presented here along with the main technologies which are included in it

### Quiz 1 - Industry development stages and digital technologies

Questions about digital technologies and industry epochs:

```{r quiz}
quiz(
  question("Industry 3.0 focuses on",
    answer("the role of people and industry in society"),
    answer("computer aided manufacturing", correct = TRUE),
    answer("discovering logistics in outer space"),
    answer("digital ecosystems")
  ),
  question("Select Digital Supply Chain technologies",
    answer("Internet of Things", correct = TRUE),
    answer("WMS"),
    answer("Cloud computing", correct = TRUE),
    answer("Virtual reality", correct = TRUE)
  )
)
```

## Blockchain and Cryptography Pt2

Some paragraphs about main blockchain concepts can be presented here

A video about cryptography:

![](https://youtu.be/8oQBij2C2ds)

To work with cryptographic functions in R we need to load `digest` library first (but it's already loaded)


```{r digest, exercise = TRUE}
library(digest)
```

Check the resulting output "hash" of encrypting word "learnr"

```{r ex1, exercise = TRUE}
digest("learnr", algo="sha256", serialize=FALSE, raw=FALSE)
```
 

Check the output, it should be:  

[1] "039a9d654e9a96bde80b89d458bb3e08e99bbcc5fe97e4103e1ea3de4828482e"

```{r quiz_c}
quiz(
  question("What are the last symbols of encrypted 'digital_literacy'?",
    answer("89d2"),
    answer("bea1"),
    answer("a3c2"),
    answer("f76c", correct = TRUE)
  )
)
```


### Quiz 2 - General Blockchain Technology Understanding

Questions about basic crypto math and technology features:

```{r quiz2}
quiz(
  question("You want to bruteforce cryptocurrency hash starting with 00000 (Hex) How many maximum attempts you will need?",
    answer("2^16"),
    answer("2^20", correct = TRUE),
    answer("2^24"),
    answer("16^10"),
    answer("16^20")
  ),
  question("What are the limitations of blockchain technology?",
    answer("It does not require centralized networks"),
    answer("High security"),
    answer("It can't be combined with usual databases"),
    answer("Additional calculations are needed", correct = TRUE)
  )
)
``` 
